\section{Introduction}

According to \cite{national}, the United States parking industry is an \$18 billion dollar industry, and there are more than 40,000 parking facilities in the United States. \cite{ibisworld} also reported that the revenue of the parking lots and garages industry has reached \$9 billion dollars, and over 136,000 employments and 8,000 businesses are involved with the industry. Although the industry has been decreasing for the past five years mostly due to the recession and under capacity of airport parking lots, \cite{ibisworld} had reported that the demand will pick up in the next five years as employment improves and demand from airports and other businesses revives. 

The access of these parking lots and garages are managed through different types of gate openers, and they are mostly operated with access card using RFID or dispensing paper tickets to customers. Although the gated parking lots and garages provide more security and guaranteed parking spaces, there are few problems to both users and the parking service providers in current systems. The most cumbersome task users have to bear with is physically swiping the access card to the reader or inserting the paper ticket to the machine to open the gate. As the result, it creates extra user actions such as finding the access card or the paper ticket, opening the window, and finally swiping the access card or inserting the paper ticket to the machine. From the service provider's perspective, it is inconvenient to issue a new access card or a paper ticket for each new client. For the access card, it is hard to retrieve or revoke expired access cards.

Through our BPM (Bluetooth Parking Manager) system, we demonstrate that users can easily use parking lots and garages with minimum user action using Bluetooth technology embedded in their smartphones. In our approach, we allow users to easily purchase parking permits through our client Android application, and seamlessly control the gates of desired parking lots and garages using Bluetooth communication channel between the user's smartphone and the Bluetooth module which controls the gate. Additionally, our approach only requires attaching a Bluetooth module to the current parking lot system, which is a low cost solution. It allows most parking lot service providers to implement the solution and improve their parking lot and garage services.